Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-18 ms.tex
error budget explanation partially re-written

\begin{multline}
\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}\sigma_{CMB}^2 + (\delta O_{\nu_i})^2 \\
+ n_{\nu_i}^2 + \sigma^2_{\nu_i, CIBA} + \sigma^2_{CO}(p)
\end{multline}

@@

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map.

>>>>

\begin{multline}
\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}^2(p) + c^2_{\nu_i}\sigma_{CMB, \nu_i}^2 + (\delta O_{\nu_i})^2 \\
+ n_{\nu_i}^2 + \sigma^2_{CIBA, \nu_i} + \sigma^2_{CO, \nu_i}(p)
\end{multline}

@@

% need to make sure to cite planckcalib paper

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term is intended to represent a 
typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
analogous term in \cite{planckdust} Equation 7 is 
($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. a term proportional to CMB model
amplitude. Because this error term's spatial dependence has the potential to 
imprint the CMB anisotropies on the derived parameters, we have chosen to 
replace \verb|SMICA|($p$) with a spatially constant, RMS value for the CMB 
amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted values of 
$\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the band 
$\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be read 
off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ represents 
the instrumental noise in the pixel of interest, and is taken to be the square 
root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
map.

% still need to explain off-diagonal terms in covariance ...
